\documentclass[11pt,reqno]{amsart}
\usepackage[left=1in,right=1in,top=1in,bottom=1.25in]{geometry}%

\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{mdwlist}
\usepackage{caption}
\usepackage{subcaption}

% AMS packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{float}
\usepackage{subfiles}

% my custom packages
\usepackage{macros}
\usepackage{packages}
\usepackage{style}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis} 

\begin{document}

\section{Introduction}

The Kawahara equation, also known as a fifth-order KdV-type equation, is used as a model for capillary-gravity water waves, magneto-acoustic waves, plasma waves, and other dispersive phenomena. This equation takes the general form
\begin{equation}\label{kawahara}
u_t + \alpha u_{xxx} + \beta u_{xxxxx} = \frac{\partial}{\partial x} f(u, u_x, u_{xxx}),
\end{equation}
where $u(x, t)$ is a real-valued function, the parameters $\alpha$ and $\beta$ are real with $\beta \neq 0$, and $f$ is a smooth function \cite{Bridges2002,Bridges2002a}. If $f$ is a variational derivative, then \cref{kawahara} is the Hamiltonian system
\[
\partial_t u = \calJ \calE'(u),
\]
where $\calJ = \partial_x$ is skew-Hermitian. The energy $\calE$ is given by
\begin{equation}\label{kawaharaE}
\calE(u) = -\frac{1}{2}\int_{-\infty}^\infty 
\left( \frac{1}{2}u_{xx}^2 - \frac{1}{2}\alpha u_x^2 + h(u, u_x, u_{xx})\right)dx,
\end{equation}
and $f$ in \cref{kawahara} is the variational derivative of the term involving $h$ in \cref{kawaharaE} \cite{Bridges2002}.

One specific example is the PDE
\begin{equation}\label{capgrav}
u_t + \frac{2}{15} \beta u_{xxxxx} - b u_{xxx}
+ 3 u u_x + 2 u_x u_{xx} + u u_{xxx} = 0,
\end{equation}
which is a weakly nonlinear long-wave approximation to the classical capillary-gravity water wave problem \cite{Sandstede2013,Champneys1997,Champneys1998}. Equation \cref{capgrav} is the Kawahara equation with $\alpha = -b$, $\beta = 2/15$, and $f(u, u_x, u_{xx}) = -(\frac{3}{2}u^2 + u u_{xx} + u_x^2)$. For simplicity, we will consider the form of the Kawahara equation from \cite{Pelinovsky2007}
\begin{equation}\label{KdV5}
u_t = u_{xxxxx} - u_{xxx} - 2 u u_x,
\end{equation}
which we will refer to as the 5th order KdV equation (KdV5). This is the Kawahara equation with $\alpha = 1$, $\beta = -1$, and $f(u, u_x, u_{xx}) = u^2$.

We are interested in traveling wave solutions of the the form $u(x, t) = u(x - ct)$. Writing \cref{KdV5} in a co-moving frame with speed $c$ by letting $\xi = x - ct$, equation \cref{KdV5} becomes
\begin{equation}\label{KdV5c}
u_t = \partial_x(u_{xxxx} - u_{xx} - u^2 + cu) ,
\end{equation}
where we have renamed the independent variable back to $x$. Equation \cref{KdV5c} is Hamiltonian, and can be written as $u_t = \partial_x \calE'(u)$, where $\calE(u)$ is the energy
\begin{equation}\label{KdV5energy}
\calE(u) = -\int_{-\infty}^{\infty} \left( \frac{1}{2}u_{xx}^2 + \frac{1}{2}u_x^2 + \frac{1}{2}cu^2 - \frac{1}{3}u^3 \right) dx.
\end{equation}
For any solution $u(x, t)$ to \cref{KdV5c}, the energy $\calE(u)$ is conserved in $t$. In additin, the energy $\calE(u)$ is translation invariant and is reversible, i.e invariant under the transformation $x \mapsto -x$.

An equilibrium solution to \cref{KdV5} satisfies the 5th order nonlinear ODE
\begin{equation}\label{KdV5eq}
u_{xxxxx} - u_{xxx} + c u_x - 2 u u_x = 0.
\end{equation}
The background state $u = 0$ is a solution to \cref{KdV5eq}. We are interested in pulses, localized solutions which decay exponentially to the background state at $\pm \infty$. Integrating \cref{KdV5eq} once, a pulse solution must also satisfy the 4th order ODE
\begin{equation}\label{KdV5eq4}
u_{xxxx} - u_{xx} + c u - u^2 = 0.
\end{equation}
Equation \cref{KdV5eq4} is Hamiltonian, with conserved quantity $H$ given by
\begin{equation}\label{KdV5ham}
H(u, u_x, u_{xx}, u_{xxx}) = u_x u_{xxx} - \frac{1}{2}u_{xx}^2 - \frac{1}{2}u_x^2 + \frac{c}{2}u^2 - \frac{1}{3}u^3,
\end{equation}
which is obtained by multiplying equation \cref{KdV5eq4} by $u_x$ and integrating once. We can also write \cref{KdV5eq4} in standard Hamiltonian form as the first order system in $\R^4$
\begin{equation}\label{KdV5ham2}
Q' = (J \nabla \tilde{H}) Q,
\end{equation}
where 
\begin{equation}\label{KdV5Q}
Q = (q_1, q_2, p_1, p_2) = (u, u_x, -u_{xxx} + u_x, u_{xx}),
\end{equation}
\begin{equation}
\tilde{H}(q_1, q_2, p_1, p_2) = \frac{1}{3}q_1^3 - \frac{1}{2}c q_1^2 + p_1 q_2 - \frac{1}{2}q_2^2 + \frac{1}{2}p_2^2,
\end{equation}
and $J$ is the standard $4 \times 4$ symplectic matrix
\[
J = \begin{pmatrix}
0 & I_2 \\ -I_2 & 0
\end{pmatrix},
\]
where $I_2$ is the $2\times 2$ identity matrix. This form is particularly useful for numerical analysis.

Linearization of the 4th order ODE \cref{KdV5eq4} about a solution $u^*(x)$ is the self-adjoint linear operator
\begin{equation}\label{KdV5hessian}
\calE''(u^*) = \partial_x^4 - \partial_x^2 + c - 2 u^* 
\end{equation}
where $\calE''(u^*)$ is the Hessian of the energy \cref{KdV5energy}. For the rest state $u^* = 0$, the eigenvalues of $\calE''(0)$ are the solutions to the fourth-order polynomial equation $\nu^4 - \nu^2 + c = 0$, which are
\begin{align*}
\nu = \pm \sqrt{ \frac{1 \pm \sqrt{1 - 4c} }{2}}.
\end{align*}
For $c > 0$, two eigenvalues have positive real part and two have negative real part, thus $u = 0$ is a hyperbolic equilibrium with a two-dimensional stable manifold and a two-dimensional unstable manifold. For $0 < c < 1/4$, all four eigenvalues are real. A bifurcation takes place at $c = 1/4$, and for $c > 1/4$, the eigenvalues of $\calE''(0)$ are a quartet $\pm \alpha_0 \pm \beta_0 i$, where $\alpha_0, \beta_0 > 0$. 

For $c > 0$, a symmetric one-pulse solution exists to \cref{KdV5eq4}. We will refer to this as the primary pulse solution. This result is stated in the following theorem, which is adapted from \cite[Theorem 2.1]{Pelinovsky2007}.

\begin{theorem}[Existence of Primary Pulse]\label{KdV1pulse}
For $c > 0$, there exists a one-pulse solution $q(x)$ to \cref{KdV5eq4} which is an even function and decays exponentially to 0 at $\pm \infty$. For the linear operators $\calE''(q)$ and $\partial_x \calE''(q)$, we have the following:
\begin{enumerate}[(i)]
\item The linear operator $\calE''(q)$ has exactly one negative eigenvalue with an even eigenfunction and a simple eigenvalue at 0 with eigenfunction $q_x$.
\item Assume that the map $c \mapsto q(x; c)$ is $C^1$ for $c > 0$. Then the linear operator $\partial_x \calE''(q)$ has an eigenvalue at 0 with algebraic multiplicity 2 and geometric multiplicity 1; the eigenfunction is $\partial_x q(x)$ and the generalized eigenfunction is $\partial_c q(x)$. 
\item Assume that 
\[
\frac{\partial}{\partial c} \left( \frac{1}{2} \int_{-\infty}^\infty q(x)^2 dx \right) > 0
\]
Then $q(x)$ is orbitally stable. This implies that $\partial_x \calE''(q)$ has no eigenvalues with positive real part.
\end{enumerate}
\end{theorem}

For $c > 1/4$, multi-pulse solutions exist to \cref{KdV5eq4}. These resemble multiple, well-separated copies of the primary pulse $q(x)$. For each $n \geq 2$, Buffoni, Champneys, and Toland \cite{Buffoni1996} show that a countable family of multi-pulse solutions exists; their proof uses the Smale horseshoe set. The result for 2-pulse solutions is also given in \cite[Theorem 2.2]{Pelinovsky2007}, which is based on the variational method used in \cite{Buffoni1996}. The method we will employ is due to Sandstede \cite{Sandstede1993, SandstedeStrut}, and uses spatial dynamics and Lin's method. The advantage of this method is that multi-pulses are constructed by splicing together consecutive copies of the primary pulse using small remainder functions. Estimates and bounds on these small remainder functions are crucial for the stability analysis. The distances between consecutive pulses are constrained to be (approximately) an integer multiple of a phase parameter which depends on $\beta_0$. Geometrically, these integers represent the number of half-twists made by the multi-pulse between consecutive peaks and represent a specific alignment of stable and unstable manifolds necessary for multi-pulses to exist.

As a first step to studying the stability of an equilibrium solution $u^*$, we will study the spectrum of the linearization of the PDE \eqref{KdV5c} about $u^*$. Substituting the standard linearization ansatz $u(x, t) = u^*(x) + \epsilon e^{\lambda t} v(x)$ into \eqref{KdV5c} and keeping terms up to order $\epsilon$, we obtain the PDE eigenvalue problem
\begin{equation}\label{KdV5PDEevp}
\partial_x \calE''(u^*) v = \lambda v.
\end{equation}
where $\calE''(u^*): H^4(\R) \subset L^2(\R) \rightarrow L^2(\R)$ is given in \cref{KdV5hessian}. We are interested in the spectrum of the linear operator $\partial_x \calE''(u^*): H^5(\R) \subset L^2(\R) \rightarrow L^2(\R)$, which is the set of $\lambda \in \C$ for which the operator $\partial_x \calE''(u^*) - \lambda \calI$ does not have bounded inverse. The essential spectrum consists of the set of all $\lambda \in \C$ for which the operator $\partial_x \calE''(u^*) - \lambda \calI$ either is not Fredholm or is Fredholm with nonzero index. For KdV5, it follows from \cite[Theorem 3.1.11]{Kapitula2013} that $\partial_x \calE''(u^*) - \lambda \calI$ cannot be Fredholm with nonzero index. Thus the essential spectrum consists of all $\lambda \in \C$ for which the operator $\partial_x \calE''(u^*) - \lambda \calI$ is not Fredholm. Since $\partial_x \calE''(u^*)$ is exponentially asymptotic to the operator 
\[
\partial_x \calE''(0) = \partial_x(\partial_x^4 - \partial_x^2 + c - 2 u^*),
\]
by the Weyl essential spectrum theorem \cite[Theorem 2.2.6]{Kapitula2013} and \cite[Theorem 3.1.11]{Kapitula2013}, $\partial_x \calE''(u^*)$ and $\partial_x \calE''(0)$ have the same essential spectrum. By a straightforward calculation, the essential spectrum of $\partial_x \calE''(u^*)$ is the entire imaginary axis. In particular, the essential spectrum does not depend on the equilibrium solution $u^*(x)$.

Spectral stability thus depends on the point spectrum, which is the set of all $\lambda \in \C$ for which $\dim \ker(\partial_x \calE''(u^*) - \lambda \calI) > 0$. Since \cref{KdV5c} is Hamiltonian, these eigenvalues must come in quartets $\{ \pm \lambda, \pm \overline{\lambda}\}$ \cite[Proposition 5.1.2]{Kapitula2013}, thus the best we can hope for is neutral stability. For an equilibrium solution $u^*(x)$, it straightforward to show that 
\begin{align*}
\partial_x \calE''(u^*) (\partial_x u^*) &= 0 \\
\partial_x \calE''(u^*) (-\partial_c u^*) &= \partial_x u^*,
\end{align*}
where for now we assume that $\partial_c u^*$ exists. Thus there is an eigenvalue at 0 with at least algebraic multiplicity 2 and geometric multiplicity 1. The kernel eigenfunction $\partial_x u^*$ is a consequence of translation invariance. For the primary pulse solution $q(x)$, these are the only eigenvalues. For an $n$-pulse solution $q_n(x)$, there will be $n-1$ additional sets of eigenvalues near 0. Since these result from nonlinear interactions between the tails of neighboring pulses, we will refer to these as interaction eigenvalues. For double pulses, Chugunova and Pelinovsky prove that there is a pair of interaction eigenvalues which is either real or purely imaginary (to leading order) with negative Krein signature \cite[Theorem 2.3]{Pelinovsky2007}. 

The presence of the essential spectrum along the entire imaginary axis makes any purely imaginary interaction eigenvalues difficult to locate. In order to do this, instead of multipulses on the real line, we will look at multi-pulses on a periodic domain. In this case, the essential spectrum becomes a discrete set of eigenvalues. For simplicity, we will refer to these as essential spectrum eigenvalues, even though they are elements of the point spectrum. This makes the analysis straightforward as long as the essential spectrum eigenvalues and the interaction eigenvalues do not interfere with each other.

\section{Mathematical Setup}

In this section, we write our problem in a general form, for which KdV5 will be a special case. SUMMARIZE THIS HERE. All proofs will be deferred to appendices.

\subsection{Hamiltonian PDE}\label{sec:HamPDE}

First, we set up a Hamiltonian PDE which is reversible and translation invariant. This analysis follows \cite{Grillakis1987}. Let $X = H^{2m}(\R)$ and $Y = L^2(\R)$. Consider the PDE
\begin{equation}\label{genPDE}
u_t = \partial_x \calE'(u)
\end{equation}
where $u \in X$ and $\calE(u): X \subset Y \rightarrow \R$ is a smooth functional representing the energy of the system. We take the following hypothesis regarding the energy $\calE(u)$.

\begin{hypothesis}\label{Ehyp}
The energy $\calE(u)$ has the following properties
\begin{enumerate}[(i)]
\item $\calE(0) = 0$ and $\calE'(0) = 0$.
\item $\calE(u)$ is reversible, i.e. $\calE(u) = \calE(\rho(u))$, where $\rho$ is the operator on $X$ defined by $[\rho(u)](x) = u(-x)$.
\item $\calE(u)$ is translation invariant, i.e. $\calE(T(s)u) = \calE(u)$ for all $s \in \R$, where $\{T(s) : s \in \R \}$ is the one parameter group of unitary operators on $X$ defined by $[T(s)]u(\cdot) = u(\cdot - s)$.
\item $\calE'(u): X \rightarrow X$ is a differential operator of the form
\begin{equation}\label{Eprimeuform}
\calE'(u) = \partial_x^{2m}u - f(u, \partial_x u, \dots, \partial_x^{2m-1} u),
\end{equation}
where $f: \R^{2m} \rightarrow \R$ is smooth.
\end{enumerate}
\end{hypothesis}

\noi\cref{Ehyp}(iv) holds in applications such as KdV5, and ensures that we can write the equilibrium equation $\partial_x \calE'(u) = 0$ as a first order system.

Differentiating the reversibility relation $\calE(u) = \calE(\rho(u))$ with respect to $u$, we have
\[
\calE'(u) = \rho^*( \calE'(\rho(u) ) = \rho( \calE'(\rho(u) ),
\]
since $\rho$ is self-adjoint. This implies that the linear part of $\calE'(u)$ only involves even-order derivatives of $u$ with respect to $x$. Differentiating the symmetry relation $\calE(T(s)u) = \calE(u)$ with respect to $u$, we have
\begin{equation}\label{Eprimesymm}
\calE'(u) = T(s)^* \calE'(T(s)u) = T(-s) \calE'(T(s)u)
\end{equation}
and
\begin{equation}\label{EHessiansymm}
\calE''(u) = T(s)^* \calE''(T(s)u) T(s).
\end{equation}
Finally, differentiating the symmetry relation $\calE(T(s)u) = \calE(u)$ with respect to $s$ at $s = 0$, 
\begin{align*}
0 = \langle \calE'(u), T'(s) u \rangle|_{s = 0}
= \langle \calE'(u), T'(0) u \rangle
= \langle \calE'(u), \partial_x u \rangle
\end{align*}
for all $u \in X$, since $T'(0) = \partial_x$ is the infinitesimal generator of the translation group $T(s)$. The energy $E(u)$ is conserved along solutions $u$ to \cref{genPDE}, since
\[
\frac{d}{dt}\calE(u) = \langle \calE'(u), u_t \rangle = \langle \calE'(u), \partial_x \calE'(u) \rangle = 0,
\]
where we used the fact that the operator $\partial_x$ is skew-symmetric. In addition, there is a second conserved quantity $V: L^2(\R) \rightarrow \R$, given by
\begin{equation}\label{defV}
V(u) = -\frac{1}{2} \int_{-\infty}^\infty u^2 dx,
\end{equation}
which represents charge in some applications. $V(u)$ is also conserved along solutions $u$ to \cref{genPDE}, since
\begin{align*}
\frac{d}{dt}V(u) &= \langle V'(u), u_t \rangle
= \langle -u, \partial_x \calE'(u) \rangle 
= \langle \partial_x u, \calE'(u) \rangle = 0,
\end{align*}
where we used $V'(u) = -u$ in the second equality.

As in \cite{Grillakis1987}, we will study bound states of \cref{genPDE}, which are solutions of the form
\begin{equation}
u(x, t) = T(ct)\phi(x) = \phi(x - ct),
\end{equation}
where $\phi \in X$. Since $T(s)$ is the translation group, these bound states are traveling waves; we will refer to these states as traveling waves from here on. If $\phi$ satisfies the equilibrium equation
\begin{equation}\label{eqODE1}
\calE'(\phi) = c V'(\phi),
\end{equation}
then $T(ct)\phi(x)$ is a traveling wave, since 
\begin{align*}
\frac{d}{dt}T(ct)\phi &= c T'(ct)\phi 
= c T'(0)T(ct)\phi \\
&= \partial_x T(ct) c V'(\phi)
= \partial_x T(ct) \calE'(\phi) \\
&= \partial_x T(ct) T(ct)^* \calE'(T(ct)\phi) \\
&= \partial_x \calE'(T(ct)\phi) 
\end{align*}
Since $V'(\phi) = -\phi$, we can write the equilibrium equation as
\begin{equation}\label{eqODE}
\calE'(\phi) + c \phi = 0.
\end{equation}
Without loss of generality, we will assume that $\calE'(\phi)$ does not contain any terms of the form $b\phi$ for $b$ constant, since those are accounted for by the $c \phi$ term in \cref{eqODE}.

We take the following hypothesis concerning existence of traveling waves. This hypothesis is similar to \cite[Assumption 2]{Grillakis1987}. In the next section, we will give a condition under which this hypothesis is satisfied. 
\begin{hypothesis}\label{cintervalhyp}
There exists an open interval $(c_1, c_2) \subset \R$ and a $C^1$ map $c \mapsto \phi_c$ such that for every $c \in (c_1, c_2)$, $\phi_c$ is a traveling wave solution for \cref{genPDE}, i.e. 
\[
\calE'(\phi_c) + c \phi_c = 0.
\]
Furthermore, $\partial_x \phi_c \neq 0$.
\end{hypothesis}

We are interested in the stability of these traveling wave solutions. As a first step in stability analysis, we will look at the spectrum of the linearization of the PDE \cref{genPDE} about a traveling wave. For $c \in (c_1, c_2)$, let $\phi_c$ be a solution to \cref{eqODE}, which is a traveling wave solution to \cref{genPDE}. Then the linearization of the PDE \cref{genPDE} about $\phi_c$ is the linear operator $\partial_x \calL(\phi_c)$, where $\calL(\phi_c)$ is defined by
\begin{equation}\label{PDElinearization}
\calL(\phi_c) = 
\calE''(\phi_c) + c
\end{equation}
and $\calE''(\phi_c)$ is the Hessian of the energy $\calE(\phi_c)$. Both $\calE''(\phi_c)$ and $\calL(\phi_c)$ are self-adjoint. Since $\phi_c$ is a traveling wave, using \cref{Eprimesymm} and \cref{eqODE}, we have
\begin{align}\label{TeqODE}
\calE'(T(s)\phi_c) + c T(s)\phi_c = T(s)[\calE'(\phi_c) + c \phi_c] = 0.
\end{align}
Differentiating \cref{TeqODE} with respect to $s$ at $s = 0$, this becomes
\begin{align*}
0 &= \calE''(T(0)\phi_c)T'(0)\phi_c + c T'(0)\phi_c \\
&= (\calE''(\phi_c) + c ) \partial_x \phi_c \\
&= \calL(\phi_c) \partial_x \phi_c
\end{align*}
Thus $\partial_x \phi_c$ is an eigenfunction of $\calL(\phi_c)$ with eigenvalue 0. Differentiating one more time, $\partial_x \phi_c$ is also an eigenfunction of $\partial_x \calL(\phi_c)$ with eigenvalue 0.

Differentiating \cref{eqODE} with respect to $c$, which we can do because the mapping $c \mapsto \phi_c$ in Hypothesis \ref{cintervalhyp} is $C^1$, we have
\begin{align*}
\calE''(\phi_c)\partial_c \phi_c + c \partial_c \phi_c + \phi_c = 0,
\end{align*}
which we can rearrange to get 
\begin{align*}
(\calE''(\phi_c) + c )(-\partial_c \phi_c) = \phi_c.
\end{align*}
Differentiating both sides, we have
\begin{align*}
\partial_x \calL(\phi_c) (-\partial_c \phi_c) 
= \partial_x (\calE''(\phi_c) + c )(-\partial_c \phi_c) = \partial_x\phi_c.
\end{align*}
Thus $-\partial_c \phi_c$ is a generalized eigenfunction of $\partial_x \calL(\phi_c)$ corresponding to eigenvalue 0.

\subsection{Traveling waves}\label{sec:travelingwaves}

We will look now look at traveling wave solutions to the PDE \cref{genPDE}, which are solutions to equilibrium equation \cref{eqODE}. To do this, we will use a spatial dynamics approach. From this viewpoint, an exponentially localized traveling wave is a homoclinic orbit connecting a rest state to itself. To do this, we write \cref{eqODE} as a first order system of ODEs in the standard way. Let $U = (u, \partial_x u, \dots, \partial_x^{2m-1} u)^T \in \R^{2m}$. Then by \cref{Ehyp}(iv), equation \cref{eqODE} is equivalent to the first order system
\begin{equation}\label{genODE}
U'(x) = F(U(x); c),
\end{equation}
where $F: \R^{2m} \times \R \rightarrow \R^{2m}$ is given by
\begin{equation}\label{defF}
F(u_1, u_2, \dots, u_{2m}; c) = 
\begin{pmatrix}
u_2 \\ u_3 \\ \vdots \\ f(u_1, u_2, \dots, u_{2m}) - c u_1
\end{pmatrix}.
\end{equation}
$F$ is smooth, and $F(0; c) = 0$ for all $c$. Reversibility implies that
\begin{equation}\label{genODErev}
F(RU; c) = -RF(U; c),
\end{equation}
where $R:\R^{2m} \rightarrow \R^{2m}$ is the standard reversor operator defined by
\begin{equation}\label{reverserR2m}
R(u_1, u_2, \dots, u_{2m-1}, u_{2m}) = (u_1, -u_2, \dots, u_{2m-1}, -u_{2m}).
\end{equation}
In particular, if $U(x)$ is a solution to \cref{genODE}, so is $RU(-x)$. Taking the derivative of \cref{genODErev} with respect to $U$, it follows that 
\begin{equation}\label{genODErevDF}
D F(RU; c) = -RDF(U; c)R.
\end{equation}
From the last component of \eqref{genODErev}, $f(RU) = f(U)$. It also follows from reversibility that $Df(RU) = RDf(U)$, which implies
\begin{equation}\label{frev}
\begin{aligned}
\partial_{u_j} f(R U) &= (-1)^{j+1} \partial_{u_j} f(U) \\
\partial^2_{u_j u_k} f(R U) &= (-1)^{j+k} \partial^2_{u_j u_k} F(U)
\end{aligned}
\end{equation}
For $U = 0$,
\begin{align}\label{fpartials0}
\partial_{u_j} f(0) &= \begin{cases}
0 & j \text{ even}\\
0 & j = 1 \\
c_j & j \text{ odd, } j > 1
\end{cases}
\end{align}
where the $c_j$ are constants. Again, we can assume without without loss of generality that $c_0 = \partial_{u_1} f(0) = 0$, since that is accounted for by the $c u_1$ term in \cref{defF}.

Next, we assume that \cref{genODE} is a conservative system.

\begin{hypothesis}\label{Hhyp}
There exists a smooth function $H: \R^{2m} \times \R \rightarrow \R$, denoted $H(U; c)$, such that 
\begin{enumerate}[(i)]
\item $H(0; c) = 0$ for all $c$
\item $\nabla_U H(U; c) = 0$ if and only if $F(U; c) = 0$
\item For all $U \in \R^{2m}$ and all $c$,
\begin{equation}
\langle \nabla_U H(U; c), F(U; c) \rangle = 0
\end{equation}
\end{enumerate}
\end{hypothesis}

\noi It follows from \cref{Hhyp} that $H$ is conserved along solutions $U(x)$ to \cref{genODE}. If $U(x)$ is such a solution, then
\[
\frac{d}{dx}H(U(x); c) = \langle \nabla H(U(x); c), U'(x) \rangle
= \langle \nabla H(U(x); c), F(U(x); c) \rangle = 0
\]

Since $F(0; c) = 0$ for all $c$, the rest state $U = 0$ is an equilibrium of \cref{genODE} for all $c$. The next hypothesis addresses the hyperbolicity of this equilibrium. We note that although the eigenvalue pattern described in \cref{hypeqhyp} is not necessary for the existence of a homoclinic orbit, it is a sufficient condition for the existence of multi-pulse solutions.

\begin{hypothesis}\label{hypeqhyp}
For a specific $c_0 \in \R$ with $c_0 > 0$, $U = 0$ is a hyperbolic equilibrium of \cref{genODE}, i.e. $DF(0; c_0)$ has no eigenvalues with real part 0. Furthermore, the spectrum of $DF(0; c_0)$ contains a quartet of simple eigenvalues $\pm \alpha_0 \pm \beta_0 i$, $\alpha_0, \beta_0 > 0$, and for any other eigenvalue $\nu$ of $DF(0; c_0)$, $|\text{Re }\nu| > \alpha_0$.
\end{hypothesis}

Let $W^s(0; c_0)$ and $W^u(0; c_0)$ be the stable and unstable manifolds of the equilibrium at 0, and let $E_0^s(c_0)$ and $E_0^u(c_0)$ be the stable and unstable eigenspaces of $DF(0; c_0)$. By reversibility, these spaces have dimension $m$. The stable and unstable manifolds are smooth since $F$ is smooth.

\subsection{Primary pulse solution}\label{sec:primarypulse}

We now address the existence of a primary pulse solution, which is a symmetric homoclinic orbit connecting the rest state equilibrium to itself. In general, the existence of such a solution is unknown, although in specific cases such as KdV5 we do have an existence result (\cref{KdV1pulse}). Thus we will take the existence of a primary pulse solution for a specific wavespeed $c_0$ as a hypothesis.

\begin{hypothesis}\label{Qexistshyp}
For the same $c_0$ as in \cref{hypeqhyp}, there exists a homoclinic orbit solution $Q(x; c_0) \in W^s(0) \cap W^u(0) \subset H^{-1}(0)$ to \cref{genODE}. In addition,
\begin{enumerate}[(i)]
\item $Q(0; c_0) \neq 0$
\item $\nabla_U H(Q(0; c_0); c_0) \neq 0$
% \item $\partial_c H(Q(0; c_0); c_0) \neq 0$
\item $Q(x; c_0)$ is symmetric with respect to the reversor operator \cref{reverserR2m}, i.e. $Q(-x; c_0) = R Q(x; c_0)$
\end{enumerate}
\end{hypothesis}

\noi Since we obtained \cref{genODE} by putting \cref{eqODE} into a first order system in the standard way, 
\begin{equation}\label{Qqrelation}
Q(x; c_0) = (q(x; c_0), \partial_x q(x; c_0), \dots, \partial_x^{2m-1}q(x; c_0))^T,
\end{equation}
where $q(x; c_0)$ is an even function and is an exponentially localized traveling wave solution solution to \cref{genPDE}. 

Next, we address the intersection of the stable and unstable manifolds $W^s(0; c_0)$ and $W^u(0; c_0)$. By \cref{Hhyp}, $W^s(0; c_0), W^u(0; c_0) \subset H^{-1}(0; c_0)$, where $H^{-1}(0; c_0)$ is the 0-level set of $H$. We have the following lemma concerning $H^{-1}(0; c_0)$.

\begin{lemma}\label{manifoldinH0}
There exists $\delta > 0$ such that for $c \in (c_0 - \delta, c_0 + \delta)$, the zero level set $H^{-1}(0; c)$ contains a smooth $(2m-1)$-dimensional manifold $K(c)$; $K(c_0)$ contains $Q(0; c_0)$.
\end{lemma}

We then take the following hypothesis regarding the intersection of the stable and unstable manifolds in $H^{-1}(0; c_0)$.

\begin{hypothesis}\label{H0transversehyp}
The stable manifold $W^s(0; c_0)$ and the unstable manifold $W^u(0; c_0)$ intersect transversely in $H^{-1}(0; c_0)$ at $Q(0; c_0)$.
\end{hypothesis}

\noi By \cref{H0transversehyp} and \cref{manifoldinH0}, 
\[
\dim (T_{Q(0; c_0)}W^s(0; c_0) + T_{Q(0; c_0)}W^u(0; c_0)) = \dim K(c_0) = 2m-1 
\]
Since $\dim T_{Q(0; c_0)}W^s(0; c_0) = m$ and $\dim T_{Q(0; c_0)}W^s(0; c_0) = m$, by a dimension-counting argument, $\dim T_{Q(0; c_0)}W^s(0; c_0) \cap T_{Q(0; c_0)}W^u(0; c_0) = 1$. Since $Q(x; c_0) \subset W^s(0; c_0) \cap W^u(0; c_0)$, 
\[
Q'(0; c_0) \in T_{Q(0; c_0)}W^s(0; c_0) \cap T_{Q(0; c_0)}W^u(0; c_0),
\]
thus we have the nondegeneracy condition
\begin{equation}\label{nondegencond}
T_{Q(0; c_0)}W^s(0; c_0) \cap T_{Q(0; c_0)}W^u(0; c_0) = \R Q'(0; c_0)
\end{equation}
 
Using \cref{nondegencond}, we decompose the tangent spaces of the stable and unstable manifolds at $Q(0; c_0)$. Since the two tangent spaces have a one-dimensional intersection spanned by $Q'(0; c_0)$, we can decompose them as 
\begin{equation}\label{TQ0decomp1}
\begin{aligned}
T_{Q(0; c_0)}W^u(0; c_0) &= \R Q'(0; c_0) \oplus Y^-(c_0) \\
T_{Q(0; c_0)}W^s(0; c_0) &= \R Q'(0; c_0) \oplus Y^+(c_0)
\end{aligned}
\end{equation}

We can now prove the existence of homoclinic orbits $Q(x; c)$ for $c$ near $c_0$ and show that $Q(x; c)$ is differentiable in $c$.

\begin{theorem}\label{transverseint}
Assume \cref{Hhyp} and \cref{H0transversehyp}. There exists $\delta > 0$ such that for $c \in (c_0 - \delta, c_0 + \delta)$, the stable and unstable manifolds $W^s(0; c)$ and $W^u(0; c)$ have a one-dimensional transverse intersection in $H^{-1}(0; c)$ which is a homoclinic orbit $Q(x; c)$. The map $c \rightarrow Q(x; c)$ is smooth. Furthermore, $\partial_c Q(x; c)$ is exponentially localized, i.e. for any $\epsilon > 0$ there exists $\delta_1 > 0$ with $\delta_1 < \delta$ such that for $c \in (c_0 - \delta_1, c_0 + \delta_1)$,
\begin{equation}\label{Qcbound}
|\partial_c Q(x; c)| \leq C e^{-(\alpha_0 - \epsilon)|x|}
\end{equation}
\end{theorem}
NOTE TO SELF: WE NEED TO ADD PROVE OF EXP LOC OF $\partial_c Q$. THIS SHOULD BE LIKE WHAT WE DID IN THE SUSPENSION BRIDGE EXAMPLE.d

Theorem \ref{transverseint} implies that Hypothesis \ref{cintervalhyp} is satisfied. From this point forward, we will fix $c = c_0$ For simplicity, we will use $c$ in place of $c_0$ and will omit the dependence on $c$ in our notation. 

\subsection{Variational equation}\label{sec:vareq1}

The variational equation is the linearization of \cref{genODE} about the primary pulse solution $Q(x)$ and will be an important tool in our analysis. The variational and adjoint variational equations associated with \cref{genODE} are
\begin{align}
V' = DF(Q(x)) V \label{vareq1} \\
W' = -DF(Q(x))^* W \label{adjvareq1},
\end{align}
where $DF(Q(x))$ is the $2m \times 2m$ matrix
\begin{equation}\label{defDF}
DF(Q(x)) = 
\begin{pmatrix}
0 & 1 & 0 & \dots & 0 & 0 \\
0 & 0 & 1 & \dots & 0 & 0 \\
& && \ddots \\
0 & 0 & 0 & \dots & 1 & 0 \\
0 & 0 & 0 & \dots & 0 & 1 \\
\partial_{u_1}f(Q(x)) - c & \partial_{u_2}f(Q(x)) & \partial_{u_3}f(Q(x)) & \dots & \partial_{u_{2m-1}}f(Q(x)) & \partial_{u_{2m}}f(Q(x))
\end{pmatrix}
\end{equation}
It follows from \cref{nondegencond} that $Q'(x)$ is the unique bounded solution to \cref{vareq1}, and that there exists a unique bounded solution $\Psi(x)$ to \cref{adjvareq1}. (In both cases, uniqueness is up to scalar multiples). Since we have a conserved quantity $H$, we know the exact form of $\Psi(x)$, which is given in the following lemma.

\begin{lemma}\label{psiform}
The solution $\Psi(x)$ is given by $\Psi(x) = \nabla H(Q(x))$. In addition, $\Psi(x)$ is symmetric with respect to the standard reversor operator $R$, i.e. $\Psi(-x) = R \Psi(x)$, and the last component of $\Psi(x)$ is $q'(x)$.
\end{lemma}

The last lemma of the section collects a few important results about solutions to the variational and adjoint variational equations.

\begin{lemma}\label{eigadjoint}
Consider the linear ODE $V' = A(x)V$ and the corresponding adjoint equation $W' = -A(x)^* W$, where $A$ is an $n \times n$ matrix depending on $x$. Then the following are true.
\begin{enumerate}[(i)]
\item $\dfrac{d}{dx}\langle V(x), W(x) \rangle = 0$, thus the inner product is constant in $x$.
\item If $W(x)$ is bounded and $V(x) \rightarrow 0$ as $x \rightarrow \infty$ or $V(x) \rightarrow -\infty$, then $\langle V(x), W(x) \rangle = 0$ for all $x \in \R$. The same holds if we reverse the roles of $W$ and $V$.
\item If $\Phi(y, x)$ is the evolution operator for $V'(x) = A(x)V(x)$, then $\Phi(x, y)^*$ is the evolution operator for the adjoint equation $W'(y) = -A(y)^* W(y)$.
\end{enumerate}
\end{lemma}

\noi From \cref{eigadjoint}(ii), $\Psi(0) \perp \R Q'(0) \oplus Y^+ \oplus Y^-$, thus we can decompose $\R^{2m}$ as
\begin{equation}\label{R2mdecomp}
\R^{2m} = \R Q'(0) \oplus Y^+ \oplus Y^- \oplus \R \Psi(0).
\end{equation}

\subsection{Spectrum of pulses}\label{sec:genspectrum}

In this section, we set up the the problem that we will use to find the eigenvalues associated with an equilibrium solution to \cref{genPDE}. Let $\phi$ be an exponentially localized traveling wave solution to \cref{genPDE}. We will study the spectrum of the linearized operator $\partial_x \calL(\phi) = \partial_x(\calE''(\phi) + c)$. First we note that the PDE eigenvalue problem
\begin{equation}\label{genPDEeig}
\partial_x \calL(\phi) v = \lambda v
\end{equation}
is equivalent to the system
\begin{equation}\label{genPDEeig2}
\begin{aligned}
\calL(\phi) v &= k \\
\partial_x k &= \lambda v
\end{aligned}
\end{equation}
It will turn out that \cref{genPDEeig2} is much more convenient for analysis.

As in \cite{Sandstede1998} and the previous section, we will take a spatial dynamics approach. To do this, we write \cref{genPDEeig2} as a first order system of ODEs. Let $U(x) = (\phi(x), \partial_x \phi(x, \dots, \partial_x^{2m-1}\phi(x), 0)^T \in \R^{2m+1}$ and let $V(x) = (v(x), \partial_x v(x), \dots, \partial_x^{2m-1} v(x), k)$. Then from \cref{Eprimeuform} and \cref{PDElinearization}, equation \cref{genPDEeig2} is equivalent to the first order system
\begin{equation}\label{PDEeigsystem}
V'(x) = A(U(x))V(x) + \lambda B V(x),
\end{equation}
where $A(U(x))$ is the $(2m+1)\times(2m+1)$ matrix
\begin{equation}\label{defAphi}
A(U(x)) = 
\begin{pmatrix}
0 & 1 & 0 & \dots & 0 & 0 & 0 \\
0 & 0 & 1 & \dots & 0 & 0 & 0\\
&  && \ddots \\
0 & 0 & 0 & \dots & 1 & 0 & 0 \\
0 & 0 & 0 & \dots & 0 & 1 & 0 \\
\partial_{u_1}f(U(x)) - c & \partial_{u_2}f(U(x)) & \partial_{u_3}f(U(x)) & \dots & \partial_{u_{2m-1}}f(U(x)) & \partial_{u_{2m}}f(U(x)) & 1 \\
0 & 0 & 0 & \dots & 0 & 0 & 0
\end{pmatrix}
\end{equation}
and $B$ is the $(2m+1) \times (2m+1)$ constant coefficient matrix
\begin{equation}\label{DefB}
B = \begin{pmatrix}0 & 0 & 0 & 0 & 0 \\0 & 0 & 0 & 0 & 0 \\  & 
\vdots & & \vdots & \\0 & 0 & 0 & 0 & 0 \\1 & 0 & 0 & 0 & 0 \end{pmatrix}.
\end{equation}
We note that the upper left $2m \times 2m$ block of $A(U(x))$ is $DF(U(x))$, which is given by \cref{defDF}. 

Since $\phi$ is exponentially localized, so is $U(x)$, thus $A(U(x))$ is exponentially asymptotic to the constant coefficient matrix $A(0)$. The following lemma describes the eigenvalues and kernel of $A(0)$.

\begin{lemma}\label{eigA0lemma}
The following hold concerning the eigenvalues of $A(0)$.
\begin{enumerate}[(i)]
\item $A(0)$ has a simple eigenvalue at 0 and a quartet of eigenvalues at $\pm \alpha_0 \pm \beta_0 i$. For any other eigenvalue $\nu$ of $A(0)$, $|\text{Re }\nu| > \alpha_0$.
\item The kernel of $A(0)$ is spanned by $V_0$ and the kernel of $A^*(0)$ is spanned by $W_0$, where
\begin{align}
V_0 &= (1/c, 0, \dots, 0, 1)^T \label{V0} \\
W_0 &= (0, 0, \dots, 0, 1)^T \label{W0}
\end{align}
and $\langle V_0, W_0 \rangle = 1$.
\item The projection on the kernel of $A(0)$ is given by
\begin{equation}\label{projkernelA0}
P_{\ker A(0)} = \langle W_0, \cdot \rangle V_0
\end{equation}
\end{enumerate} 
\end{lemma}

Since $A(0)$ is not hyperbolic, the results of \cite{Sandstede1998} do not apply. Let $W^s(0)$, $W^u(0)$, and $W^c(0)$ be the stable, unstable, and center manifolds of the equilibrium at 0. By reversibility, $\dim W^s(0) = m$ and $\dim W^u(0) = m$. The center manifold $W^c(0)$ is one-dimensional.

Let $\tilde{Q}(x)$ be the primary pulse solution from \cref{sec:primarypulse}, and define $Q(x) \in R^{2m+1}$ by $Q(x) = (\tilde{Q}(x), 0)$. The variational and adjoint variational equations associated with \cref{PDEeigsystem} are
\begin{align}
V'(x) = A(Q(x)) V(x) \label{vareq2} \\
W'(x) = -A(Q(x))^* W(x) \label{adjvareq2}
\end{align}
where we reuse the same notation $V$ and $W$ for convenience. Since 
\begin{align*}
(\partial_x \calL(q))\partial_x q &= 0 \\
(\partial_x \calL(q))(-\partial_c q) &= \partial_x q,
\end{align*}
it follows that 
\begin{align}
(\partial_x Q(x))' &= A(Q(x))(\partial_x Q(x)) \label{Qprimevarsol} \\
(\partial_c Q(x))' &= A(Q(x))(\partial_c Q(x)) + B(\partial_x Q(x))\label{Qcvarsol}
\end{align}
Thus $\partial_x Q(x)$ is an exponentially localized solution to the variational equation \eqref{vareq2}.

Since $Q(x)$ is exponentially localized, it cannot involve the center manifold $W^c(0)$, thus it must lie in the intersection of the stable and unstable manifolds. In particular, this implies that $\R Q'(0) \subset T_{Q(0)}W^s(0) \cap T_{Q(0)}W^u(0)$. It follows from \cref{H0transversehyp} that these are actually equal, which we state in the following lemma.

\begin{lemma}\label{nondegenlemma}
We have the nondegeneracy condition
\begin{equation}\label{nondegen2}
T_{Q(0)}W^s(0) \cap T_{Q(0)}W^u(0) = \R Q'(0)
\end{equation}
\end{lemma}

\noi Using the nondegeneracy condition \eqref{nondegen2}, we can decompose the tangent spaces of the stable and unstable manifolds at $Q(0)$ as
\begin{align*}
T_{Q(0)}W^s(0) &= \R Q'(0) \oplus Y^+ \\
T_{Q(0)}W^u(0) &= \R Q'(0) \oplus Y^- \\
\end{align*}
Since $\dim \R Q'(0) \oplus Y^+ \oplus Y^- = 2m-1$, there we need two more directions to span $\R^{2m+1}$. To find these, we will use the following lemma regarding solutions to \eqref{vareq2} and \eqref{adjvareq2}.

\begin{lemma}\label{varadjsolutions}
We have the following solutions to the variational equation and adjoint variational equation.
\begin{enumerate}
	\item There exists a bounded solution $V^c(x)$ to \eqref{vareq2} such that 
	\begin{equation}
	V^c(x) \rightarrow V_0 \text{ as }|x| \rightarrow \infty
	\end{equation}
	$V^c$ is symmetric with respect to the standard reversor operator $R$, i.e. $V^c(-x) = R V^c(x)$. Furthermore, $V^c = (\tilde{V}^c, 1)$, where $\tilde{V}^c$ solves $\tilde{V}^c(x)' = DF(Q(x)) \tilde{V}^c(x) + (0, \dots, 0, 1)^T$.

	\item There exist two linearly independent, bounded solutions $\Psi(x)$ and $\Psi^c(x)$ to \eqref{adjvareq2}.
	\begin{enumerate}[(i)]
	\item $\Psi(x)$ is the exponentially localized solution
	\begin{equation}\label{psicomponents}
	\Psi(x) = (\nabla H(Q(x)), q(x)).
	\end{equation}
	$\Psi(x)$ is symmetric with respect to the standard reversor operator $R$, i.e. $\Psi(-x) = R \Psi(x)$. 
	\item $\Psi^c(x)$ is the constant solution
	\begin{equation}
	\Psi^c(x) = W_0
	\end{equation}
	\end{enumerate}
	Any other bounded solution to \eqref{adjvareq2} is a linear combination of these. Finally, $\Psi(0), \Psi^c(0) \perp \R Q'(0) \oplus Y^+ \oplus Y^-$.
\end{enumerate}
\end{lemma}

\begin{remark}\label{remark:computeVc}
If $v^c(x)$ is the first component of $V^c(x)$, $v^c$ is a formal solution to $\calL(q) v_c = 1$. Since
\[
V^c(x) = (v^c(x), \partial_x v^c(x), \dots, \partial_x^{2m-1}v^c(x), 1 ),
\]
this provides a convenient way of computing $V^c(x)$ numerically. We also note that since $v^c(x)$ is not in $H^{2m}(\R)$, $v^c(x)$ is not an eigenfunction of \cref{genPDEeig}.
\end{remark}

\begin{remark}\label{remark:psinotation}
We note that for convenience we have used the notation $Q(x)$ and $\Psi(x)$ in both \cref{sec:primarypulse} and \cref{sec:genspectrum} to denote the primary pulse and the localized solution to the adjoint variational equation. Since we will be considering the existence and the stability problem separately, this should not cause confusion. In addition, the inner products $\langle \Psi(x), Q(y) \rangle$ and $\langle \Psi(x), Q'(y) \rangle$ are the same.
\end{remark}

Using Lemma \ref{nondegenlemma} and Lemma \ref{varadjsolutions}, we can decompose $\R^{2m+1}$ as  
\begin{equation}
\R^{2m+1} = \R \Psi(0) \oplus \R \Psi^c(0) \oplus \R Q'(0) \oplus Y^+ \oplus Y^-
\end{equation}
where $\R \Psi(0) \oplus \R \Psi^c(0) \perp \R Q'(0) \oplus Y^+ \oplus Y^-$.

Before we conclude this section, we will make one final hypothesis concerning a higher order Melnikov integral. First, we note that the standard Melnikov integral is 0, i.e. 
\begin{equation}\label{M1}
M_1 = \int_{-\infty}^\infty \langle \Psi(x), B Q'(x) \rangle =
\int_{-\infty}^\infty q(x) \: \partial_x q(x)  = 0
\end{equation}
since the last component of $\Psi(x)$ is $q(x)$ by Lemma \ref{varadjsolutions}, and $q(x)$ is an even function. Since we have a Hamiltonian system, this is the expected result. We take the following hypothesis regarding a higher order Melnikov integral.
\begin{hypothesis}\label{Melnikov2hyp}
The following higher order Melnikov integral is nonzero.
\begin{equation}\label{M2}
M = \int_{-\infty}^\infty \langle \Psi(x), B Q_c(x) \rangle dx =
\int_{-\infty}^\infty q(x) q_c(x) dx \neq 0
\end{equation}
\end{hypothesis}
In applications such as KdV5, numerical analysis suggests that \cref{Melnikov2hyp} is satisfied with $M > 0$.

\bibliographystyle{amsalpha}
\bibliography{kdv5.bib}

\end{document}
