\documentclass[10pt,reqno]{amsart}
\usepackage[left=1in,right=1in,top=1in,bottom=1.25in]{geometry}%

\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{mdwlist}
\usepackage{caption}
\usepackage{subcaption}

% AMS packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{float}
\usepackage{subfiles}

% my custom packages
\usepackage{macros}
\usepackage{packages}
\usepackage{style}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis} 

\numberwithin{theorem}{section}
\numberwithin{equation}{section}

\begin{document}

\section{Krein bubble}

\subsection{Block matrix for periodic 2-pulse}

Using the symmetry of the periodic 2-pulse, the block matrix $S(\lambda)$ and the determinant $E(\lambda) = \det S(\lambda)$ has the following form.

\begin{lemma}\label{lemma:2blockmatrix}
For a periodic 2-pulse, the block matrix $S(\lambda)$ is the $4 \times 4$ matrix
\begin{align}\label{dpSmatrix}
S(\lambda) = 
\begin{pmatrix}
e^{-\nu(\lambda)X_1} & -e^{\nu(\lambda)X_0} & \tilde{M}^c \lambda^2 & 0 \\
-e^{\nu(\lambda)X_1} & e^{-\nu(\lambda)X_0} & 0 & \tilde{M}^c \lambda^2 \\
\frac{1}{2}\lambda M^c e^{-\nu(\lambda)X_1} & \frac{1}{2}\lambda M^ce^{\nu(\lambda)X_0} &-a-\lambda^2 M & a \\
\frac{1}{2}\lambda M^c e^{\nu(\lambda)X_1} & \frac{1}{2}\lambda M^c e^{-\nu(\lambda)X_0}  & a & -a-\lambda^2 M
\end{pmatrix} + R(\lambda)
\end{align}
where
\begin{equation}\label{2pa}
a = \langle \Psi(X_0), Q'(-X_0) \rangle + \langle \Psi(X_1), Q'(-X_1) \rangle.
\end{equation}
The remainder matrix is a $4 \times 4$ matrix of the form
\begin{align}
R(\lambda)
\begin{pmatrix} 
c_1(\lambda) & \tilde{c}_1(\lambda) & \lambda d_1(\lambda) & \lambda \tilde{d}_1(\lambda) \\ 
-c_1(-\lambda) & -\tilde{c}_1(-\lambda) & -\lambda \tilde{d}_1(-\lambda) & -\lambda d_1(-\lambda) \\ 
c_2(\lambda) & \tilde{c}_2(\lambda) & d_2(\lambda) & \tilde{d}_2(\lambda) \\ 
-c_2(-\lambda) & -\tilde{c}_2(-\lambda) & \tilde{d}_2(-\lambda) & d_2(-\lambda)
\end{pmatrix},
\end{align}
where the individual entries have bounds
\begin{align*}
|c_1|, |\tilde{c}_1| &\leq C (|\lambda| + r^{1/2})^2, \quad |d_1|, |\tilde{d}_1| \leq C (|\lambda| + r^{1/2})^2 \\
|c_2|, |\tilde{c}_2| &\leq C (|\lambda| + r^{1/2})^2, \quad |d_2|, |\tilde{d}_2| \leq C (|\lambda| + r^{1/2})^3
\end{align*}
In addition,
\begin{equation}\label{2pblockmatrixdet}
\begin{aligned}
\det S(&\lambda, r) = -2 \lambda^2 (2a + \lambda^2 M + R_1) \left( M \sinh(\nu(\lambda)X) + \lambda (M \tilde{M} - M^c \tilde{M}^c) \cosh(\nu(\lambda)X) \right) \\
&-4 a \lambda^3 M^c \tilde{M}^c \sinh(\nu(\lambda)X_1)\sinh(\nu(\lambda)X_0) 
+ R_2 \lambda^2 \sinh(\nu(\lambda)(X_1 - X_0)) + \lambda^2 R_3 \sinh(\nu(\lambda)X)) + \lambda^3 R_4,
\end{aligned}
\end{equation}
where the $R_i$ are scalars with bounds 
\begin{equation*}
|R_1| \leq C r^{3/2}, \quad |R_2|, |R_3|, |R_4| \leq C(|\lambda| + r^{1/2})^4,
\end{equation*}
and $\det S(-\lambda) = -\det S(\lambda)$.
\end{lemma}

The Krein bubble occurs when first essential spectrum eigenvalue (positive Krein signature) collides with imaginary interaction eigenvalue (negative Krein signature) on the imaginary axis. These are, to leading order, given by
\begin{align*}
\lambda_1 &= c \frac{\pi i}{X + c \frac{M\tilde{M} - M^c\tilde{M^c}}{M}} \\
\lambda_* &= \sqrt{-\frac{2a}{M}}.
\end{align*}
Recall that $X = X_0 + X_1$, and we can change $X$ by changing $X_1$ without changing the scaling factor $r$. $X_0$ and $X_1$ are related, but for sufficiently large $X_1$, varying $X_1$ produces essentially no change in $X_0$. Thus since $\lambda_* = \mathcal{O}(e^{-\alpha X_0}) = \mathcal{O}(r^{1/2})$, $\lambda_*$ is essentially constant for what we will be doing. Also we assume $\lambda_*$ is purely imaginary, since that is the interesting case.

We will need something a little better for $\lambda_*$. Since the remainder term $R_1 = \mathcal{O}(r^{3/2})$ and (importantly) does not depend on $\lambda$, take instead
\begin{equation}\label{lambdastar}
\lambda_* = \sqrt{-\frac{2a - R_1 }{M}} = \sqrt{-\frac{2a}{M}} + \mathcal{O}(r).
\end{equation}
which will eliminate a term we don't want later.

Change variables by letting $\mu = \nu(\lambda)$. For sufficiently small $\lambda$, we then have
\begin{equation}\label{lambdamu}
\lambda = \nu^{-1}(\mu) = c \mu + \mathcal{O}(\mu^3),
\end{equation}
which gives us the expression
\begin{equation}\label{det2}
\begin{aligned}
\det S(&\mu, r) = -2 c^2 \mu^2 (2a + c^2 \mu^2 M + R_1) \left( M \sinh(\mu X) + c \mu K \cosh(\mu X) \right) \\
&-4 a c^3 \mu^3 M^c \tilde{M}^c \sinh(\mu X_1)\sinh(\mu X_0) 
+ R_2 \mu^2 \sinh(\mu(X_1 - X_0)) + \mu^2 R_3 \sinh(\mu X) + \mu^3 R_4,
\end{aligned}
\end{equation}
where $K = M \tilde{M} - M^c \tilde{M}^c$. Since we are looking for nonzero eigenvalues, we can divide by $c^2 \mu^2$ to solve
\begin{equation}\label{det3}
\begin{aligned}
-2 (&2a + c^2 \mu^2 M + R_1) \left( M \sinh(\mu X) + c \mu K \cosh(\mu X) \right) \\
&-4 a c \mu M^c \tilde{M}^c \sinh(\mu X_1)\sinh(\mu X_0) 
+ R_2 \sinh(\mu(X_1 - X_0)) + R_3 \sinh(\mu X) + \mu R_4 = 0
\end{aligned}
\end{equation}
where $K = M \tilde{M} - M^c \tilde{M}^c$.

\subsection{Leading order terms}

Since the Krein bubble is centered around the imaginary essential spectrum eigenvalue, let $\mu_* = \lambda_* / c$ and $\mu_1 = \lambda_1 /c$. For our ansatz, we take
\[
\mu = \mu_* + h
\]
The maximum radius of the Krein bubble happens when $\lambda_1 = \lambda_*$. We can always choose $X$ so that this occurs. Define the parameter $k$ by
\[
\mu_1 = \mu_* - k i,
\]
so that 
\[
\mu = \mu_1 + k i + h.
\]
The parameter $k$ measures the distance between $\mu_1$ and $\mu_*$ on the imaginary axis. The maximum radius will occur when $k = 0$. 

We now substitute our ansatz into \cref{det2}. First, we have
\[
2a + c^2 \left(\mu_* + h \right)^2 M + R_1 = 2 c^2 M \mu_* h  + M c^2 h^2.
\]
We note that our choice of $\lambda_*$ eliminates $R_1$ here, which is key. Expanding the denominator of $\mu_1$ in a Taylor series,
\begin{align*}
\mu_1 &= \frac{\pi i}{X\left(1  + c \frac{K}{M X} \right) }
= \frac{\pi i}{X}\left( 1 - c \frac{K}{M X} + c^2 \frac{K^2}{M^2 X^2} + \mathcal{O}\left(\frac{1}{X^3}\right) \right).
\end{align*}
Substituting $\mu = \mu_1 + k i + h$ and expanding the $\sinh$ and $\cosh$ terms in a Taylor series about $\pi i$,
\begin{align*}
\sinh(\mu X) &= \sinh\left( \pi i - c \frac{K \pi i }{M X} + c^2 \frac{K^2 \pi i }{M^2 X^2} + (h + k i)X + \mathcal{O}\left(\frac{1}{X^3}\right) \right) \\
&= (-1)\left( - c \frac{K \pi i }{MX} + c^2 \frac{K^2 \pi i }{M^2 X^2} + (h + k i)X \right) + \mathcal{O}\left( \left(\frac{1}{X} + (h + k) X \right)^3 \right)
\end{align*}
and
\begin{align*}
\cosh(\mu X) &= \cosh\left( \pi i - c \frac{K \pi i }{M X} + c^2 \frac{K^2 \pi i }{M^2 X^2} + (h + k i)X + \mathcal{O}\left(\frac{1}{X^3}\right) \right) \\
&= (-1) + \mathcal{O}\left( \left(\frac{1}{X} + (h + k)X \right)^2 \right)
\end{align*}
Thus we have
\begin{align*}
M \sinh(&\mu X) + c \mu K \cosh(\mu X) \\
&= -M \left( -c \frac{K \pi i }{MX} + c^2 \frac{K^2 \pi i }{M^2 X^2} + (h + k i)X \right) + \mathcal{O}\left( \left(\frac{1}{X} + (h + k)X \right)^3 \right) \\
&- K \left( \frac{c \pi i}{X} - c^2 \frac{K \pi i}{M X^2} + c^3 \frac{K^2 \pi i}{M^2 X^3} + c (h + k i) + \mathcal{O}\left(\frac{1}{X^3}\right) \right)\left( -1 + \mathcal{O}\left( \left(\frac{1}{X} + (h + k)X \right)^2 \right) \right) \\
&= -\left( M + \frac{c K}{X}\right)(h+ki)X + \mathcal{O}\left( \left( \frac{1}{X} + (h+k)X \right)^3 \right)
\end{align*}

\subsection{Rescaling}

Anticipating what we will get in the end, we take the following rescaling.
\begin{align*}
\mu_* &= r^{1/2} \tilde{\mu} \\
h &= r X_0 \tilde{h} / X^{1/2} \\
k &= r X_0 \tilde{k} / X^{1/2}
\end{align*}
Since $\mu_1$ is close to $\mu_*$, $1/X = \mathcal{O}(r^{1/2})$, thus $\sinh(\mu X) =  \mathcal{O}(r^{1/2})$. Furthermore, 
\begin{align*}
\sinh(\mu&(X_1 - X_0)) = \sinh(\mu(X - 2 X_0)) \\
&= \sinh(\mu X) \cosh(2 \mu X_0)  - \cosh(\mu X)\sinh(2 \mu X_0) \\
&= \mathcal{O}\left( r^{1/2} + r^{1/2} X_0 \right) 
= \mathcal{O}\left( r^{1/2}|\log r| \right) 
\end{align*}
Finally, 
\begin{align*}
\sinh(\mu &X_1)\sinh(\mu X_0) = \sinh(\mu ( X - X_0 )) \sinh(\nu(\lambda)X_0) \\
&= \left( \sinh(\mu X) \cosh( \mu X_0)  - \cosh(\mu X)\sinh(\mu X_0) \right)\sinh(\mu X_0) \\
&= \mu_*^2 X_0^2 + \mathcal{O}(r^{1/2})
\end{align*}

Substituting these into \cref{det3} and simplifying, we wish to solve
\begin{equation}\label{det4}
\begin{aligned}
2 &\left( 2 c^2 M \tilde{\mu} \tilde{h} \frac{X_0}{X^{1/2}} r^{3/2} \right) 
\left( \left( M + \frac{c K}{X} \right) ( \tilde{h}+ \tilde{k} i) \frac{X_0}{X^{1/2}} r X + \mathcal{O}(r^{3/2}) \right) 
+ 2 M M^c \tilde{M}^c c^3 \tilde{\mu}^5 r^{5/2} X_0^2 + \mathcal{O}( r^{5/2} |\log r| ) = 0
\end{aligned}
\end{equation}
Dividing by $X_0^2 r^{5/2}$, noting that $X_0 = \mathcal{O}(|\log r|)$ and $1/X = \mathcal{O}(r^{1/2})$ and simplifying, we obtain the equation
\begin{equation}\label{det5}
\begin{aligned}
\tilde{h} ( \tilde{h}+ \tilde{k} i) 
+ \frac{M^c \tilde{M}^c }{2 M} c \tilde{\mu}^4 + \mathcal{O}\left( \frac{1}{|\log r|} \right) = 0,
\end{aligned}
\end{equation}
where we used the fact that $1/|\log r|$ is lower order than $r^{1/2}$. 

This means that
\begin{itemize}
	\item We should be able to prove the Krein bubble occurs and have the leading order term for the radius. Everything higher order than \cref{term1} should not contribute.
	\item For numerics, the leading order term \cref{term1} is accurate to a relative error of 0.075.
	\item We can get a better numerical result if we toss in one of the terms we know is in $b$
	\item We might be able to use a symmetry argument or somesuch to figure out which terms in $b$ contribute at this order, although it is unclear how helpful this will be.
\end{itemize}





\end{document}